RNA-seq from 4 cell populations

### 2021-07-28 deconvolution/fans4/molec_profiling.Rmd
bug fix

# cd /hpc/users/hoffmg01/work/cmc_analysis/src
cd /hpc/users/hoffmg01/work/CMC/covarr-de/deconvolution/fans4
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

fitBasic = dream( vobj, form, info, L=L, BPPARAM=SnowParam(36, progressbar=TRUE))
```

>>>>

# cd /hpc/users/hoffmg01/work/cmc_analysis/src
cd /hpc/users/hoffmg01/work/CMC/covarr-de/deconvolution/fans4
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
export OMP_NUM_THREADS=1
R

@@

fitBasic = dream( vobj, form, info, L=L, BPPARAM=SnowParam(12, progressbar=TRUE))
```
